Hydras \& Co.

### 2023-05-08 doc/chap-intro-goedel.tex

@@

% ici

\section{The reason behind this work}

  \begin{itemize}
  \item Historical interest on G\"{o}del's proof
  \item Many popularization publications, \emph{e.g.}
    \cite{smullyan1992godel, Hofstadter1999Godel, GoedelCassou}, vs. technical complexity of the full proof .

    \begin{quote}
      The purpose of a proof is \emph{understanding}.
      Efim Zelmanov in~\cite{mathproof}.  
          \end{quote}
        \item O'Connor's proof was written at the end of \coq V7, rewritten at the beginning of \coq V8. Since then, \coq and its ecosystem evolved a lot (new styles, tactics, documentation tools).
          We think this evolution should benefit
          to the original proof-scripts and make their understanding easier.
        \end{itemize}

\section{Historical context}
Russel O'Connor's work is the first computer verified proof 
the essential incompleteness of arithmetic.

\begin{todo}
Reference to previous/later implementations.
\end{todo}

>>>>

It was the first computer verified proof 
the essential incompleteness of arithmetic.
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

Several reasons --- enumerated below --- led us to maintain and document this work in the framework of 
Coq community~\cite{CoqCommunity}.

 \begin{itemize}
 \item Historical interest on G\"{o}del's proof and its mechanizations, as shown by the numerous litterature on this topic
   (for instance \cite{smullyan1992godel, Hofstadter1999Godel, GoedelCassou}).

  \item O'Connor's proof was written at the end of \coq V7, then rewritten at the beginning of \coq V8. Since then, \coq and its ecosystem evolved a lot (new styles, tactics, documentation tools).
          We think this evolution should benefit
          to the original proof-scripts and make their understanding easier.

        \item Finally, let us quote  Efim Zelmanov in~\cite{mathproof}
             \begin{quote}
      The purpose of a proof is \emph{understanding}.

    \end{quote}
    We hope that underlying some points of the proof will
     make easier to understand this large and technical work.

        \end{itemize}

        For technical reasons --- mainly in order to make easier the installation and use of its sub-libraries, we split the project
into two main parts: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

@@

### 2023-05-08 doc/schutte-chapter.tex
missing space

\begin{itemize}
\item It allows us to give a \emph{name} (using \texttt{Definition}) two witnesses 
of existential quantifiers (let us recall that, in classical logic, one may consider non-constructive proofs of existential statements)
\item By separating definitions from proofs of [unique] existence, one may make definitions  more concise and readable. Look for instance at 
the definitions of  \texttt{zero}, \texttt{succ}, \texttt{plus}, etc. in the rest of this chapter.
\end{itemize}
%%%% ICI ICI

@@

Let us call  $\phi_0$ the ordering function of \texttt{AP}.
In the mathematical text, we shall use indifferently the notations  $\omega^\alpha$ and$\phi_0(\alpha)$.

>>>>

\begin{itemize}
\item It allows us to give a \emph{name} (using \texttt{Definition}) to witnesses 
of existential quantifiers (let us recall that, in classical logic, one may consider non-constructive proofs of existential statements)
\item By separating definitions from proofs of [unique] existence, one may make definitions  more concise and readable. Look for instance at 
the definitions of  \texttt{zero}, \texttt{succ}, \texttt{plus}, etc. in the rest of this chapter.
\end{itemize}
%%%% ICI ICI

@@

Let us call  $\phi_0$ the ordering function of \texttt{AP}.
In the mathematical text, we shall use indifferently the notations  $\omega^\alpha$ and $\phi_0(\alpha)$.
